yield response function

### 2025-08-29 codes/R/visualized_results.qmd
Results visualization changed to include true yield

```{r}
plot_yield_response(model = "NO_ANN", n_fields = 5)     # uses N
plot_yield_response(model = "DO_ANN", n_fields = 5)     # uses N_tilde 
plot_yield_response(model = "SO_ANN", n_fields = 10) 
plot_yield_response(model = "NO_RF", n_fields = 5) 
plot_yield_response(model = "SO_RF", n_fields = 5) 
```
# RMSE

>>>>

```{r}
# plot_yield_response(model = "NO_ANN", n_fields = 5)     # uses N
# plot_yield_response(model = "DO_ANN", n_fields = 5)     # uses N_tilde 
# plot_yield_response(model = "SO_ANN", n_fields = 10) 
# plot_yield_response(model = "NO_RF", n_fields = 5) 
# plot_yield_response(model = "SO_RF", n_fields = 5)

models_to_compare <- c("NO_ANN", "DO_ANN", "SO_ANN", "NO_RF", "SO_RF")

# compute global limits for you
plot_yield_response("NO_ANN", 1, global_models = models_to_compare)
plot_yield_response("NO_ANN", 5, global_models = models_to_compare)
plot_yield_response("NO_ANN", 10, global_models = models_to_compare)
plot_yield_response("DO_ANN", 1, global_models = models_to_compare)
plot_yield_response("DO_ANN", 5, global_models = models_to_compare)
plot_yield_response("DO_ANN", 10, global_models = models_to_compare)
plot_yield_response("SO_ANN", 1, global_models = models_to_compare)
plot_yield_response("SO_ANN", 5, global_models = models_to_compare)
plot_yield_response("SO_ANN", 10, global_models = models_to_compare)
plot_yield_response("NO_RF",  1, global_models = models_to_compare)
plot_yield_response("NO_RF",  5, global_models = models_to_compare)
plot_yield_response("NO_RF",  10, global_models = models_to_compare)
plot_yield_response("SO_RF",  1, global_models = models_to_compare)
plot_yield_response("SO_RF",  5, global_models = models_to_compare)
plot_yield_response("SO_RF",  10, global_models = models_to_compare)
```
# RMSE
